Lab 5: Optimization

### 2023-02-15 Lab 5  Optim/Lab5_Optim.Rmd
Add files via upload

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}

#first generate our data (remember to set the seed)

set.seed(123)
x <- rpois(100, 5)
xbar <- mean(x)
n <- length(x)

@@

Funcall <- function(f, ...) f(...)
Iterate <- function(f, n = 1) {
        function(x) {
                Reduce(Funcall, rep.int(list(f), n), x, right = TRUE)
        }
}

@@

g <- Vectorize(g, "n") #vectorize our iterator with respect to n
iterates <- g(10, 1:7)

@@

Here we can see that across the 7 iterations, we get closer and closer to the root (which is 5.1). The algorithm continues (for as many iterations as you specify) until the parameter values stabilize, or $\theta_{n+1}$ and $\theta_{n}$ become approximately equal, and the root is approximated. If this doesn't make sense to you, watch \href{https://www.youtube.com/watch?v=-5e2cULI3H8}{this video}.

@@

\newpage
#Practice on your own:
Now, on your own, try doing this with `mtcars` data, instead of generated data. Let's say we want to set our $y$ value as `mpg`, $x1$ as `wt`, and $x2$ as `gear`.

>>>>

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}
#first generate our data (remember to set the seed)
set.seed(123)
x <- rpois(100, 5) #sample from a poisson
xbar <- mean(x) #mean of the poisson samples
n <- length(x) #n obs

#Here we will create several nested functions

@@

Funcall <- function(f, ...) f(...) #Remember the dots! The dots operator allows you to pass an arbitrary number of additional arguments that aren't explicitly defined in the function

Iterate <- function(f, n = 1) {
        function(x) {
                Reduce(Funcall, rep.int(list(f), n), x, right = TRUE)
        }
}

@@

g <- Vectorize(g, "n") #vectorize our iterator with respect to n

#calling the function g that we created above to find g(x)
iterates <- g(10, 1:7)

@@

Here we can see that across the 7 iterations, we get closer and closer to the root (which is 5.1). The algorithm continues (for as many iterations as you specify) until the parameter values stabilize, or $\theta_{n+1}$ and $\theta_{n}$ become approximately equal, and the root is approximated. If this doesn't make sense to you, watch [this video](https://www.youtube.com/watch?v=-5e2cULI3H8).

@@

\newpage
# Practice on your own:
Now, on your own, try doing this with `mtcars` data, instead of generated data. Let's say we want to set our $y$ value as `mpg`, $x1$ as `wt`, and $x2$ as `gear`.
